Positive Relationship between a Country's Employment Rate and Permanent Immigrant Inflows

### 2023-04-04 outputs/paper/paper.qmd
changes to the introduction

In this paper, we will examine the relationship between a country's employment rate and permanent immigrant inflows through a linear regression analysis, providing insights into the factors that influence permanent immigrant inflows and guiding governments in developing policies to attract and retain permanent immigrants. Specifically, we will focus on 5 countries with relatively high immigration numbers (United States, Canada, United Kingdom, Australia, and Japan). We will draw data from the OECD website. Our respondents of interest are the percentage of the working-age population, as they represent the potential labor force and have a significant impact on a country's economic growth and development.

>>>>

In this paper, we will examine the relationship between a country's employment rate and permanent immigrant inflows through a linear regression analysis, The estimand here that we’re trying to estimate is the correlation of employment rate and permanent immigrants inflows. Specifically, we will focus on 5 countries with relatively high immigration numbers (United States, Canada, United Kingdom, Australia, and Japan). We will draw data from the OECD website. Our respondents of interest are the percentage of the working-age population, as they represent the potential labor force and have a significant impact on a country's economic growth and development.
